Jeff Goldsmith

### 2018-06-09 software.Rmd
typo fixes
updating subpage stylesheets so academicons work throughout

<link rel="stylesheet" href="styles.css" type="text/css" />

@@

## refund

@@

## refund.shiny

@@

Code for several projects are developed on [GitHub](https://github.com/jeff-goldsmith):

>>>>

<link rel="stylesheet" href="styles.css" type="text/css" />
<link rel="stylesheet" href="academicons/css/academicons.min.css"/>

@@

## `refund`

@@

## `refund.shiny`

@@

Code for several projects has been developed on [GitHub](https://github.com/jeff-goldsmith):
